---
title: "Germany WVS"
author: "Camille Robertson"
date: "2023-04-06"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Import data into DataFrame
```{r}
library(readr)

wvs <- read_csv("WVS Cross-National Wave 7.csv")
```

Create variable with only German observations
```{r}
germany <- wvs[wvs$B_COUNTRY_ALPHA == "DEU",]
```

View values for each variable question
```{r}
table(germany$Q121)
table(germany$Q50)
table(germany$Q250)
table(germany$Q57)
```
Create new column for Q121 without negative values
```{r}
germany$immigration <- NA
germany$immigration[germany$Q121 >= 1 & germany$Q121 <= 5] <- germany$Q121[germany$Q121 >= 1 & germany$Q121 <= 5]

table(germany$immigration)

```

Create new column for Q50 without negative values
```{r}
germany$financial <- NA
germany$financial[germany$Q50 >= 1 & germany$Q50 <= 10] <- germany$Q50[germany$Q50 >= 1 & germany$Q50 <= 10]

table(germany$financial)
```

Create new column for Q250 without negative values
```{r}
germany$democracy <- NA
germany$democracy[germany$Q250 >= 1 & germany$Q250 <= 10] <- germany$Q250[germany$Q250 >= 1 & germany$Q250 <= 10]

table(germany$democracy)
```

Create a new column for trust variable with binary values
```{r}
germany$trust <- NA
germany$trust[germany$Q57 == 1] <- 1
germany$trust[germany$Q57 == 2] <- 0

table(germany$trust)
```


Create a dataframe with each new column
```{r}
germany_data <- data.frame(germany$immigration, germany$financial, germany$democracy, germany$trust)
colnames(germany_data) <- c("Immigration", "Financial", "Democracy", "Trust")
```

Create a logistic regression model with trust as dependent variable
```{r}
model <- glm(Trust ~ Immigration + Financial + Democracy, data = germany_data, family = "binomial")
summary(model)
```

Visualize logistic regression model with table
```{r}
library(jtools)
library(huxtable)

export_summs(model, error_format = "(p = {p.value})", model.names = "Model", 
             coefs = c("Views on Immigration" = "Immigration",
                       "Financial Satisfaction" = "Financial",
                       "Belief in Democracy" = "Democracy"))
```

Calculate the Odds Ratios for each of the independent variables
```{r}
library(gt)

coef <- c(coefficients(model)[["Immigration"]], coefficients(model)[["Financial"]],
          coefficients(model)[["Democracy"]])

or <- exp(coef)

variables <- c(variable.names(model)[2:4])

odds_ratio <- data.frame(variables, coef, or)
colnames(odds_ratio) <- c("Independent Variable", "Coefficient", "Odds Ratio")

odds_ratio
```

Make some prediction using the logistic model for different values of the independent variables
```{r}
df <- data.frame(Immigration = seq(min(germany_data$Immigration, na.rm = TRUE),
                                   max(germany_data$Immigration, na.rm = TRUE),
                                   len = 500),
                 Financial = seq(min(germany_data$Financial, na.rm = TRUE),
                                 max(germany_data$Financial, na.rm = TRUE),
                                 len = 500),
                 Democracy = seq(min(germany_data$Democracy, na.rm = TRUE),
                                 max(germany_data$Democracy, na.rm = TRUE),
                                 len = 500))

df$Predict <- predict(model, df, type = "response")
```

Plot the sigmoid function

```{r}
library(ggplot2)

ggplot(germany_data, aes(x = Immigration, y = Trust)) + 
  labs(x = "Views on Immigration", y = "Pr(Generalized Trust)") +
  theme_light(base_family = "Times New Roman", base_size = 12) + geom_point(shape = 1) + 
  stat_smooth(method = "glm", method.args = list(family="binomial"), color = "darkseagreen4",
              fill = "darkseagreen3")
```

```{r}
ggplot(germany_data, aes(x = Financial, y = Trust)) + 
  labs(x = "Financial Satisfaction", y = "Pr(Generalized Trust)") +
  theme_light(base_family = "Times New Roman", base_size = 12) + geom_point(shape = 1) + 
  scale_x_continuous(breaks = seq(1, 10, 1)) +
  stat_smooth(method = "glm", method.args = list(family="binomial"), color = "darkseagreen4",
              fill = "darkseagreen3")
```

```{r}
ggplot(germany_data, aes(x = Democracy, y = Trust)) + 
  labs(x = "Belief in Democracy", y = "Pr(Generalized Trust)") +
  theme_light(base_family = "Times New Roman", base_size = 12) + geom_point(shape = 1) + 
  scale_x_continuous(breaks = seq(1, 10, 1)) +
  stat_smooth(method = "glm", method.args = list(family="binomial"), color = "darkseagreen4",
              fill = "darkseagreen3")
```



```{r}
plot(Trust ~ Immigration, data = germany_data,
     xlab = "Views on Immigration",
     ylab = "Pr(Generalized Trust)",
     family = "Times New Roman")
lines(Predict ~ Immigration, df, lwd = 3, col = "darkseagreen3")
```

```{r}
plot(Trust ~ Financial, data = germany_data,
     xlab = "Financial Satisfaction",
     ylab = "Pr(Generalized Trust)",
     family = "Times New Roman")
lines(Predict ~ Financial, df, lwd = 3, col = "darkseagreen3")
```

```{r}
plot(Trust ~ Democracy, data = germany_data,
     xlab = "Belief in Democracy",
     ylab = "Pr(Generalized Trust)",
     family = "Times New Roman")
lines(Predict ~ Democracy, df, lwd = 3, col = "darkseagreen3")
```

```{r}
library(pscl)
pR2(model)["McFadden"]
```

