---
title: "Robustness"
author: "Camille Robertson"
date: "2023-04-25"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Import and Clean Data

```{r}
library(readr)

# import data from csv file and subset germany data
wvs <- read_csv("WVS Cross-National Wave 7.csv")
germany <- wvs[wvs$B_COUNTRY_ALPHA == "DEU",]
```

```{r}
# clean the immigration question from negative values
germany$immigration <- NA
germany$immigration[germany$Q121 >= 1 & germany$Q121 <= 5] <- 
  germany$Q121[germany$Q121 >= 1 & germany$Q121 <= 5]

# validate values
table(germany$immigration)

# clean the financial question from negative values
germany$financial <- NA
germany$financial[germany$Q50 >= 1 & germany$Q50 <= 10] <- 
  germany$Q50[germany$Q50 >= 1 & germany$Q50 <= 10]

# validate values
table(germany$financial)

# clean the democracy question from negative values
germany$democracy <- NA
germany$democracy[germany$Q250 >= 1 & germany$Q250 <= 10] <- 
  germany$Q250[germany$Q250 >= 1 & germany$Q250 <= 10]

# validate values
table(germany$democracy)

# create a binary variable from the trust question
germany$trust <- NA
germany$trust[germany$Q57 == 1] <- 1
germany$trust[germany$Q57 == 2] <- 0

table(germany$trust)
```
### Visualization

```{r}
color <- c("lightblue2", "darkseagreen2", "slategray3", "lavenderblush2", "pink2")
borders <- c("lightblue3", "darkseagreen3", "slategray4", "lavenderblush3", "pink3")

# display the range of responses for each question

barplot(table(germany$immigration), col = color, border = borders,
        xlab = "Response Choices",
        ylab = "Number of Responses",
        family = "Times New Roman")
```

```{r}
barplot(table(germany$financial), col = color, border = borders,
        xlab = "Response Choices",
        ylab = "Number of Responses",
        family = "Times New Roman")
```

```{r}
barplot(table(germany$democracy), col = color, border = borders,
        xlab = "Response Choices",
        ylab = "Number of Responses",
        family = "Times New Roman")
```

Create a data set with only the columns we will be focusing on:
```{r}
germany_data <- data.frame(germany$immigration, germany$financial, germany$democracy, germany$trust)
colnames(germany_data) <- c("Immigration", "Financial", "Democracy", "Trust")

# display a statistical summary for each variable
summary(germany_data$Immigration)
summary(germany_data$Financial)
summary(germany_data$Democracy)
```

## Logistic Regression

```{r}
# create a logistic regression model with trust as the response variable
model <- glm(Trust ~ Immigration + Financial + Democracy, data = germany_data, family = "binomial")
summary(model)
```


## Robustness

### Model 2
```{r}
# create a new independent variable for views on income equality
table(germany$Q106)

germany$income <- NA
germany$income[germany$Q106 >= 1 & germany$Q106 <= 10] <- germany$Q106[germany$Q106 >= 1 & germany$Q106 <= 10]

#validate values
table(germany$income)

# add column to germany data set
germany_data = cbind(germany_data, germany$income)
colnames(germany_data)[5] <- "Income_Equality"
```

Create another logistic regression model with the additional variable
```{r}
model2 <- glm(Trust ~ Immigration + Financial + Democracy + Income_Equality, data = germany_data, 
              family = "binomial")
summary(model2)
```

### Model 3
```{r}
# create a new independent variable for levels of education
table(germany$Q275)

germany$education <- NA
germany$education[germany$Q275 >= 0 & germany$Q275 <= 8] <- germany$Q275[germany$Q275 >= 0 & germany$Q275 <= 8]

# validate values
table(germany$education)

# add column to germany data set
germany_data = cbind(germany_data, germany$education)
colnames(germany_data)[6] <- "Education"
```

Create another logistic regression model with the additional variable
```{r}
model3 <- glm(Trust ~ Immigration + Financial + Democracy + Income_Equality + Education, 
              data = germany_data, 
              family = "binomial")
summary(model3)
```

### Pseudo R-Squared
```{r}
library(pscl)
pR2(model)
pR2(model2)
pR2(model3)
```

## Comparison of Models
```{r}
library(jtools)
library(huxtable)

# create a table to visualize the contrast between the models
export_summs(model, model2, model3, error_format = "", 
             model.names = c("Model 1", "Model 2", "Model 3"), 
             coefs = c("Views on Immigration" = "Immigration",
                       "Financial Satisfaction" = "Financial",
                       "Belief in Democracy" = "Democracy",
                       "Views on Income Equality" = "Income_Equality",
                       "Level of Education" = "Education"))
```

### Coefficients and Odds Ratios
```{r}
library(gt)

# get the coefficients from each model
coefs_model1 <- c(coef(model)[["Immigration"]], coef(model)[["Financial"]],
                  coef(model)[["Democracy"]], NA, NA)

coefs_model2 <- c(coef(model2)[["Immigration"]], coef(model2)[["Financial"]],
                  coef(model2)[["Democracy"]], coef(model2)[["Income_Equality"]], NA)

coefs_model3 <- c(coef(model3)[["Immigration"]], coef(model3)[["Financial"]],
                  coef(model3)[["Democracy"]], coef(model3)[["Income_Equality"]],
                  coef(model3)[["Education"]])

# calculate the odds ratio for each variable in each model
OR_model1 <- exp(coefs_model1)
OR_model2 <- exp(coefs_model2)
OR_model3 <- exp(coefs_model3)

# get all the variable names for the column
Variable <- c(variable.names(model3)[2:6])

# create a data frame with the coefficients and odds ratios
coef_OR <- data.frame(Variable, coefs_model1, OR_model1, coefs_model2, OR_model2, coefs_model3,
                      OR_model3)
```

Organize the coefficients and odds ratios for each model in a table
```{r}
coef_OR_tbl <- gt(coef_OR)
coef_OR_tbl <- 
  coef_OR_tbl |>
  tab_spanner(
    label = "Model 1",
    columns = c(coefs_model1, OR_model1)
  ) |>
  tab_spanner(
    label = "Model 2",
    columns = c(coefs_model2, OR_model2)
  ) |>
  tab_spanner(
    label = "Model 3",
    columns = c(coefs_model3, OR_model3)
  ) |>
  cols_label(
    coefs_model1 = "Coefficient",
    OR_model1 = "Odds Ratio",
    coefs_model2 = "Coefficient",
    OR_model2 = "Odds Ratio",
    coefs_model3 = "Coefficient",
    OR_model3 = "Odds Ratio"
  ) |>
  fmt_number(
    columns = 2:7,
    decimals = 2
  )

coef_OR_tbl
```

